---
title: "Statistics_Project_1"
author: "David Rodden"
date: "April 1, 2017"
output: pdf_document
---
  
```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
require(mosaic); require(mosaicData); require(gridExtra)
library("mosaic", lib.loc="~/R/win-library/3.3")
library("gridExtra", lib.loc="~/R/win-library/3.3")
library(readxl)
```
```{r}
sheet = read_excel("MTH_361_Project_1_Data.xlsx")
```
*Part 1: Clearly state what you are investigating*
  
We are investigating Portland's Trail Blazers' scores and verifying whether their scores at home games are greater than those of away games. The population is the Trail Blazer's games, and the quantitative variable is the points scored in each game.

$H_0: \mu_{home} = \mu_{away}$
  
$H_a: \mu_{home} > \mu_{away}$
  
*Part 2: Describe clearly how you collect your data*
  
The group opted to use data from the 2015-2016 Trail Blazer season. We collected the data by recording the points scored for home games and then the points scored at away games. The bias lies in the selection of only one team and one season; which, does not represent the entire league. The data is not paired.

*Part 3: Collect your data*
```{r}
home = sheet$home; away = sheet$away
home.mean = mean(home); away.mean = mean(away)
home.mean; away.mean
home.sd = sd(home); away.sd = sd(away)
home.sd; away.sd
home.size = length(home); away.size = length(away)
```

Verify conditions of the test:

$n_{home} \geq 30$ and $n_{away} \geq 30$. Our data passes and the Central Limit Theorem applies.

`r home.size` $\geq 30$ and `r away.size` $\geq 30$.

The mean for home games is `r home.mean` while the away game mean is `r away.mean`.
As for standard deviation, the statistics are `r home.sd` and `r away.sd`, respectively.

```{r}
summary(sheet)
histo.home = histogram(home, fit="normal", width=5, center=.5)
histo.away = histogram(away, fit="normal", width=5, center=.5)
grid.arrange(histo.home, histo.away, ncol=1)
```
Examining the histograms, it can be seen that home's data has a larger mean than the away's. In addition, the density of the datapoints contained within home's histogram is higher than that of away's.


```{r}
difference.test = t.test(home, away, data=sheet)
p.value = difference.test$p.value / 2
```


*Part 3: Describe your data*

Our p-value $\approx$ `r p.value`, which is less than our $\alpha=0.05$. Hence, we reject the null hypothesis in favor of the alternate hypothesis.


*Part 4: Create a confidence interval for the difference in means between your two groups*

```{r}
difference.conf = confint(difference.test); difference.conf
```

Our 95% confidence interval for this t-test is (`r round(difference.conf$lower, 4)`, `r round(difference.conf$upper, 4)`). This signifies that we are 95% confident that TrailBlazers score more at home games than they do at away games. This is due to the fact that the values are greater than 0.

*Part 5: Conduct a hypothesis test for a difference in means between the two groups*

To reiterate, our p-value $\approx$ `r p.value`. Our evidence from the data collected implies that, on average, the TrailBlazers score more at home games than they do at away games. Therefore, we can reject the null hypothesis at a 5% significance level. 

*Part 6: Describe what each group member did*

As a team, we worked on coordinating meeting times and discussing potential topics. During the meetings, Michael and Khang collected data and recorded it. After research, we discussed and analyzed it as a team. Following this, we began writing the markdown file. Every now and then, we knitted the file in order to make sure the project was in pristine condition. All data was protected by David Rodden's decision to upload resources to GitHub (https://github.com/DavidRodden/Statistics_Project_A). If any questions were had, Michael would follow up with the instructor for clarification.